### 2013-05-20 Publications/2013-TMI/06-results.tex
Included multivariate formulations in #67
Added some new adapted formulations.

\begin{figure}
\begin{tabular}{ccccc}
\includegraphics[width=0.19\textwidth]{model1result_b_1} &
\includegraphics[width=0.19\textwidth]{model1result_b_2} &
\includegraphics[width=0.19\textwidth]{model1result_b_3} &
\includegraphics[width=0.19\textwidth]{model1result_b_4} &
\includegraphics[width=0.19\textwidth]{model1result_b_5} \\
\includegraphics[width=0.19\textwidth]{IPMI2013-011} &
\includegraphics[width=0.19\textwidth]{IPMI2013-012} &
\includegraphics[width=0.19\textwidth]{IPMI2013-013} &
\includegraphics[width=0.19\textwidth]{IPMI2013-014} &
\includegraphics[width=0.19\textwidth]{IPMI2013-015} \\
%\includegraphics[width=0.19\textwidth]{model1result_a_1} &
%\includegraphics[width=0.19\textwidth]{model1result_a_2} &
%\includegraphics[width=0.19\textwidth]{model1result_a_3} &
%\includegraphics[width=0.19\textwidth]{model1result_a_4} &
%\includegraphics[width=0.19\textwidth]{model1result_a_5} \\
\end{tabular}
\caption{First row presents several slices along Z axis of the distorted \gls{fa} map and
the undistorted \gls{wm}-\gls{gm} and \gls{wm}-\gls{csf} contours given as shape priors,
subjected to the shift of [5.0,10.0,-5.0] mm. described in \autoref{sec:simulated_dwi}.
Second row contains the same map, now with the contours after joint segmentation-registration.}
\label{fig:fa}
\end{figure}

>>>>

%\begin{figure}
%\begin{tabular}{ccccc}
%\includegraphics[width=0.19\textwidth]{model1result_b_1} &
%\includegraphics[width=0.19\textwidth]{model1result_b_2} &
%\includegraphics[width=0.19\textwidth]{model1result_b_3} &
%\includegraphics[width=0.19\textwidth]{model1result_b_4} &
%\includegraphics[width=0.19\textwidth]{model1result_b_5} \\
%\includegraphics[width=0.19\textwidth]{IPMI2013-011} &
%\includegraphics[width=0.19\textwidth]{IPMI2013-012} &
%\includegraphics[width=0.19\textwidth]{IPMI2013-013} &
%\includegraphics[width=0.19\textwidth]{IPMI2013-014} &
%\includegraphics[width=0.19\textwidth]{IPMI2013-015} \\
%%\includegraphics[width=0.19\textwidth]{model1result_a_1} &
%%\includegraphics[width=0.19\textwidth]{model1result_a_2} &
%%\includegraphics[width=0.19\textwidth]{model1result_a_3} &
%%\includegraphics[width=0.19\textwidth]{model1result_a_4} &
%%\includegraphics[width=0.19\textwidth]{model1result_a_5} \\
%\end{tabular}
%\caption{First row presents several slices along Z axis of the distorted \gls{fa} map and
%the undistorted \gls{wm}-\gls{gm} and \gls{wm}-\gls{csf} contours given as shape priors,
%subjected to the shift of [5.0,10.0,-5.0] mm. described in \autoref{sec:simulated_dwi}.
%Second row contains the same map, now with the contours after joint segmentation-registration.}
%\label{fig:fa}
%\end{figure}

### 2013-05-20 Publications/2013-TMI/08-appendix-01.tex
Started with #67.
Just a couple of (unfinished) formulae
Included multivariate formulations in #67
Added some new adapted formulations.

>>>>

In the probabilistic approach to image segmentation, the smoothness constraints
can be introduced into the \gls{map} criterium as a \gls{mrf}. Accordingly to the
Hammersley-Clifford theorem (\textbf{FIXME}: citations needed), an \gls{mrf} can
be equivalently characterized by a Gibb's distribution:
\begin{equation}
P(\mathbf{K})=\underset{i}{\prod} Z(U)^{-1}\,e^{-U(\mathbf{x}_i \mid \beta,K)} = \mathit{const.}\,e^{- \sum\limits_i \left( U(\mathbf{x}_i \mid \beta,K) \right) } \sim e^{-\nu_B \left| K \right| }.
\end{equation}
This way, we include the assumption that the total length of the edge set $K$ is small
and we draw the equivalence with the \gls{mrf} modeling, for $U(\mathbf{x}_i \mid \beta,K)$
being the Potts model.

In the probabilistic approach, the underlying concept to segmenting an image is the
Bayes' rule. For a discrete image of $N$ pixels indexed by $i$, this rule reads as
follows:
\begin{equation}
P(K|I)=P(I \mid K)\, P(K)=\underset{i}{\prod} p (\mathbf{x}_i | K ) \, p_i(K).
\end{equation}
The normalizer probability $P(I)$ has been ommited for simplicity.

In order to express the likelihood as an absolute energy in our variation framework,
the \textit{log}-likelihood is computed:
\begin{equation}
E(K)= -\log( P(K|I) ) = \sum\limits_k \int_{\Omega_k} -\log p_k(I(\mathbf{x}),\mathbf{x}) \,d\mathbf{x}+\nu_B \left|K\right|,
\end{equation}
where $\mathbf{s} = I(\mathbf{x})$, $\mathbf{s} \in \mathbb{R}^C$ (a vector of $C$ scalar features).
Additionally, the discrete grid of $N$ pixels has been converted to a continuous space by assuming
$d\mathbf{x}$ as infinitesimal bin size.

To explicitly define the likelihood, we firstly define the squared \textit{Mahalanobis distance} that
is the exponential of a multivariate normal distribution:
\begin{equation}
\Delta^2_k (\mathbf{s}) = (\mathbf{s} - \boldsymbol{\mu}_k)^T \, \Sigma^{-1}_k \, (\mathbf{s} - \boldsymbol{\mu}_k).
\end{equation}

Therefore, the likelihood is defined as follows:
\begin{equation}
p_k(I(\mathbf{x}),\mathbf{x}) = p_k(\mathbf{s},\mathbf{x})= p_k(\mathbf{s}) = \frac{1}{ \sqrt{(2\pi)^{C}\,\left|\boldsymbol{\Sigma}_{k}\right|}}\,{e^{\left(-\frac{1}{2}  \Delta^2_k (\mathbf{s}) \right)}}.
\end{equation}

Introducing this definition on (14), we have:
\begin{equation}
E(K)= \sum\limits_k \int_{\Omega_k} -\log{\left[ \frac{1}{ \sqrt{(2\pi)^{C}\,\left|\boldsymbol{\Sigma}_{k}\right|}}\,e^{\left(-\frac{1}{2}  \Delta^2_k (\mathbf{s}) \right)} \right] } \,d\mathbf{x}+\nu_B \left|K\right|.
\end{equation}

\begin{equation}
E(K) = \sum\limits_k \int_{\Omega_k} \left( \frac{1}{2} \log{ \left( (2\pi)^{C}\,\left|\boldsymbol{\Sigma}_{k}\right| \right)} + \frac{1}{2}  \Delta^2_k (\mathbf{s}) \right) \,d\mathbf{x}+\nu_B \left|K\right|
\end{equation}

\begin{equation}
E(K) = \sum\limits_k \left( \frac{ V_k }{2} \log{ \left( (2\pi)^{C}\,\left|\boldsymbol{\Sigma}_{k}\right| \right)}+ \frac{1}{2} \int_{\Omega_k} \Delta^2_k (\mathbf{s}) \,d\mathbf{x}+\nu_B \left|K\right| \right)
\end{equation}
